### 2016-04-26 Manuscript/Demonstrations/demonstrations.tex
Add a folder for demonstration and another for script used to draw thesis pictures.

% \documentclass[11pt, draft, twoside]{report}
% \documentclass[12pt, twoside]{report}
\documentclass[12pt, oneside]{report}

% ------------------------------------------------------------------------------
% Packages import
% ------------------------------------------------------------------------------
% Text font pack
\usepackage[OT1, T1]{fontenc}              % .pdf Encoding spec
\usepackage[utf8]{inputenc}                % .tex Encoding spec
\usepackage[greek, french]{babel}          % language used
\usepackage{csquotes}                      % Ensure correct quote text
\usepackage[dvipsnames, svgnames]{xcolor}  % Color support
\frenchspacing                             % French typo
\frenchbsetup{StandardLists=true}          % Turn off french bulleted lists
\usepackage[scaled]{beramono}

% Template packages
\usepackage[top=2cm,
            bottom=2cm,
            left=2cm,
            right=2cm,
            a4paper]{geometry}             % Page layout support
\usepackage{bookmark}                      % load hyperref internaly
\usepackage{appendix}                      % Appendix package to add sub-annex | annex to main table
\hypersetup{
    pdfkeywords={Passive,
                 Optimisation,
                 Solaire,
                 Système combiné},         % list of keywords
    unicode=true,                          % non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,                       % show Acrobat’s toolbar?
    pdfmenubar=true,                       % show Acrobat’s menu?
    pdffitwindow=false,                    % window fit to page when opened
    pdfstartview={FitH},                   % fits the width of the page to the window
    pdftitle={Outil d’aide à la décision
              pour la construction de
              maison passives
              100\% solaires},             % title
    pdfauthor={Jérémy Bois},               % author
    pdfsubject={Optimisation,
                Maison passive},           % subject of the document
    pdfcreator={Jérémy Bois},              % creator of the document
    pdfproducer={Jérémy Bois},             % producer of the document
    pdfnewwindow=true,                     % links in new PDF window
    colorlinks=true,                       % false: boxed links; true: colored links
    linkcolor=black!30!orange!70,          % color of internal links (change box color with linkbordercolor)
    citecolor=magenta,                     % color of links to bibliography
    filecolor=magenta,                     % color of file links
    urlcolor=cyan                          % color of external links
}

% Scientist support
\usepackage{siunitx}                                % Unit package
\usepackage{amsmath, amssymb}                       % Allow adding complex equations
\usepackage{nicefrac}                               % for \nicefrac macro
% \usepackage{listings}                             % Code block support
\usepackage[algoruled,
            linesnumbered,
            algosection]{algorithm2e}               % Algorithm support

% Bibliography support
\usepackage[style=authoryear,
            sorting=none,
            backend=biber]{biblatex}                % Bibliography support
\addbibresource{Bibliographie/references.bib}       % Where to find bibliography

\begin{document}

\chapter*{Expression analytique de la distribution de Lévy stable et symétrique}

\chapter*{Estimation de la variance pour une marche aléatoire}

\chapter*{Autres notes}

\begin{equation}\label{eq:moyenne_generale}
    x_{m} = \left[ \frac{1}{n} \sum_{i=1}^{n}(x_{i}^{m})\right]^{\nicefrac{1}{m}}\\
\end{equation}
\begin{align}\label{eq:parametre_m}
    & m \to \infty  & \text{maximum of } x_{i}\\
    & m \to -\infty & \text{minimum of } x_{i}\\
    & m = 2         & \text{moyenne quadratique (RMS)}\\
    & m = 1         & \text{moyenne arithmétique}\\
    & m = -1        & \text{moyenne harmonique}\\
    & m \to 0       & \text{moyenne géométrique}\\
\end{align}

\end{document}