### 2017-03-16 Manuscript/Chapitres/Introduction.tex
Add build instruction in top of files. Correct biblatex weird error. Continue chapter 3 rewritting.

%!TEX root = ../main.tex

Oui c’est ça c’est l’introduction ...