### 2017-04-28 Manuscript/Nomenclature/lettres_grecques.tex
Add nomenclature structure and clean thesis classes configuration. Add config file for nomencl package.

%!TEX root = ../main.tex
% Nomenclature/lettre_grecques.tex

\nomenclature{$ae$}{Speed of light in a vacuum inertial frame
    \nomunit{\SI[per-mode=symbol]{299972443}{\meter\per\second}}}

\nomenclature{$ss$}{Planck constant
    \nomunit{\SI[per-mode=symbol]{299972443}{\meter\per\second}}}