### 2017-05-03 Manuscript/Annexes/ssc.tex
Add class definition for thesis. Clean preamble. Correct citation typo. Refactoring of build process.

\begin{figure}
    \begin{center}
            \includegraphics[page=4]{Ressources/Images/Modelisation/circulateur.pdf}
    \end{center}
    \caption{Fiche technique du circulateur \textit{Wilo-YonosECO 25/1-5 BMS}.
             \label{fig:caracs_pompes}}
\end{figure}

\begin{figure}
    \begin{center}
            \includegraphics[page=1]{Ressources/Images/Modelisation/Radco_308C_HP_plan.pdf}
    \end{center}
    \caption{Certification $ICC-SRCC$ pour le capteur \textit{Radco 308C HP}.
             \label{fig:caracs_radco}}
\end{figure}

\begin{figure}
    \begin{center}
            \includegraphics[page=1]{Ressources/Images/Modelisation/SkyPro_12_CPC58_tube.pdf}
    \end{center}
    \caption{Certification $ICC-SRC$C pour le capteur \textit{Sky Pro 12 CPC58}.
             \label{fig:caracs_skypro}}
\end{figure}