### 2017-05-27 Manuscript/Annexes/meta-modele.tex
Figure for meta-model added.

%!TEX root = ../main.tex
% Annexes/sensibilite.tex

\ttodo{Ajouter impact variation caractéristique pour estimer capteur et vitrages}