### 2017-07-07 Manuscript/Annexes/ssc.tex
Add power from EnergyPlus and Modelica. Correct error in figure and add list of models used.

%!TEX root = ../main.tex
% Annexes/ssc.tex

\begin{figure}
    \centering
    \includegraphics[page=4]{Ressources/Images/Modelisation/circulateur.pdf}
    \caption{Fiche technique du circulateur \textit{Wilo-YonosECO 25/1-5 BMS}.
             \label{fig:caracs_pompes}}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[page=1]{Ressources/Images/Modelisation/Radco_308C_HP_plan.pdf}
%     \caption{Certification $ICC-SRCC$ pour le capteur \textit{Radco 308C HP}.
%              \label{fig:caracs_radco}}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/SkyPro/din_skyPro.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Kloben Sky Pro 12 CPC58}.
             \label{fig:caracs_skypro}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/IDMK/din_idmk.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Sonnenkraft IDMK-25AL}.
             \label{fig:caracs_idmk}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/Eco/din_eco.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Dima Energy + Eco}.
             \label{fig:caracs_eco}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/CPCStar/din_CPCStar.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Ritter CPC $14$ Star}.
             \label{fig:caracs_star}}
\end{figure}