### 2017-08-21 Manuscript/Annexes/sensibilite.tex

%!TEX root = ../main.tex
% Annexes/sensibilite.tex

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_0.pdf}
    \caption[Résultat de l’analyse de Morris pour les indicateurs principaux
             ($f(\mu) = \sigma$)]
            {Résultat de l’analyse de Morris pour les indicateurs principaux
             ($f(\mu) = \sigma$).}
    \label{fig:objectifs_mu}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_star_2.pdf}
    \caption[Résultat de l’analyse de Morris sur le détail de la
             $Prod_{sol}^{CH}$ ($f(\mu^{*}) = \sigma$)]
            {Résultat de l’analyse de Morris sur le détail de la
             $Prod_{sol}^{CH}$ ($f(\mu^{*}) = \sigma$).}
    \label{fig:prod_sol_chauffage_mu_star}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_2.pdf}
%     \caption[Résultat de l’analyse de Morris sur le détail de la
%              $Prod_{sol}^{CH}$ ($f(\mu) = \sigma$)]
%             {Résultat de l’analyse de Morris sur le détail de la
%              $Prod_{sol}^{CH}$ ($f(\mu) = \sigma$).}
%     \label{fig:prod_sol_chauffage_mu}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_star_3.pdf}
%     \caption[Résultat de l’analyse de Morris sur le détail de la
%              $Conso_{app}$ ($f(\mu^{*}) = \sigma$)]
%             {Résultat de l’analyse de Morris sur le détail de la
%              $Conso_{app}$ ($f(\mu^{*}) = \sigma$).}
%     \label{fig:conso_app_mu_star}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_3.pdf}
    \caption[Résultat de l’analyse de Morris sur le détail de la
             $Conso_{app}$ ($f(\mu) = \sigma$)]
            {Résultat de l’analyse de Morris sur le détail de la
             $Conso_{app}$ ($f(\mu) = \sigma$).}
    \label{fig:conso_app_mu}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_star_4.pdf}
%     \caption[Résultat de l’analyse de Morris sur le détail de la
%              $Prod_{sol}^{valorisée}$ ($f(\mu^{*}) = \sigma$)]
%             {Résultat de l’analyse de Morris sur le détail de la
%              $Prod_{sol}^{valorisée}$ ($f(\mu^{*}) = \sigma$).}
%     \label{fig:prod_sol_valorisee_mu_star}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Ressources/Images/Sensibilite/sigma_mu_4.pdf}
    \caption[Résultat de l’analyse de Morris sur le détail de la
             $Prod_{sol}^{valorisée}$ ($f(\mu) = \sigma$)]
            {Résultat de l’analyse de Morris sur le détail de la
             $Prod_{sol}^{valorisée}$ ($f(\mu) = \sigma$).}
    \label{fig:prod_sol_valorisee_mu}
\end{figure}